Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-25 draft/chicago-spatial-covid-draft.tex
Update chicago-spatial-covid-draft.tex

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.
The relevant results are given in Figure \ref{fig:ode_results}.
We obtained the optimal ODE model parameters for Chicago from 1,000 optimizations that compared model predictions to jointly the number of cumulative infected and the deceased, as in Equation \ref{eq:obj}.

>>>>

\section{Results}
\subsection{ODE Model}
We begin by discussing the zero-dimensional model for Chicago.
Data for the progression of the pandemic in Chicago were obtained from the Chicago Data Portal \cite{Chicago_2021}.
The relevant results are given in Figure \ref{fig:ode_results}.
We obtained the optimal ODE model parameters for Chicago from 1,000 optimizations (implemented in MATLAB via the \verb|fminsearch| function)
that compared model predictions to jointly the number of cumulative infected and the deceased, as in Equation \ref{eq:obj}.
For each optimization, the initial guess for each parameter was uniformly sampled within a pre-specified range.
The parameter ranges were determined from epidemiological information.

Upon performing the optimizations we find that the fitting yields the results summarized in Table \ref{tab:parameters}.
We show the median parameters, as well as the interquartile range, and the range of variation used to sample the parameters.
Model predictions (with median parameter values, solid blue lines) are compared graphically to data (black dots) in Figure \ref{fig:ode_results}.
